### 2024-05-11 thesis/chapters/appendix/B-technical-documentation.tex
Complete technical docs

\item \textbf{eda-pumps.ipynb}
\item \textbf{eda-standing-fan.ipynb}
\item \textbf{extraction-mafaulda.ipynb}
\item \textbf{extraction-pumps.ipynb}
\item \textbf{feature-summary.ipynb}
\item \textbf{iit-src-paper.ipynb}
\item \textbf{knn-batch.ipynb}
\item \textbf{knn-mafaulda.ipynb}
\item \textbf{knn-online.ipynb}
\item \textbf{wavelets.ipynb}
\end{itemize}

>>>>

\item \textbf{eda-pumps.ipynb} - It visualizes amplitude histograms and frequency spectrum of every time series in the Pump dataset next to one another.  Spectrograms of selected situations are depicted, such as rotation speed up or slow down. This notebook is instrumental in spotting patterns between different places and dates and checking for signal clipping.

\item \textbf{eda-standing-fan.ipynb} - Estimate the rotational speed of the standing fan based on the audio recording and compare it to the estimate from vibrations. The accelerometer is attached to the back, side, and front of the shaft.

\item \textbf{extraction-mafaulda.ipynb} - Feature extraction of a complete set of features from the entire MaFaulDa in time and frequency domain (TD and FD sets) to CSV files. Enable variable \emph{EXTRACT} to proceed with a lengthy calculation that takes around ten minutes for each set. When the extraction flag is disabled, the notebook loads the already extracted files with attributes.

\item \textbf{extraction-pumps.ipynb} - Feature extraction of a complete set of features from Pump datatset in time and frequency domain (TD and FD sets) to CSV files. Enable variable \emph{EXTRACT} to proceed with calculation.

\item \textbf{feature-summary.ipynb} - Count the occurrences of predictors in the best triplets over setup experimental conditions. Feature selection techniques produce bar charts with different orderings. The explained variance of complete feature sets is shown alongside the separability of clusters measured by silhouette score. This notebook generates CSV files of the best feature sets used in \emph{knn-batch.ipynb}.

\item \textbf{iit-src-paper.ipynb} - Run the experiments described in IIT.SRC 2024 paper in Appendix~\ref{appendix:iit-src-paper}. Set variables \emph{USE\_ONE\_AXIS} and \emph{MAFAULDA\_ LABEL\_METHOD} to one of the allowed options to generate all possible results. Running the experiments and not reading precomputing results requires enabling \emph{GENERATE} variable. Additionally, the hyperparameters of the model can be changed to tune the accuracy.

\item \textbf{knn-batch.ipynb} - Train k-NN classifiers with k = 5 on three members' best subsets of features found in \emph{feature-summary.ipynb}. Evaluate a wide range of performance metrics. Plot relation of k-neighbours on error rate for subset picked by the rank product method.

\item \textbf{knn-mafaulda.ipynb} - The results of the experiments are described in the Exploratory analysis of MaFaulDa and the evaluation chapter. The setup of experimental scenarios for batch and incremental learning is followed by scales of features and their correlations. Every combination of parameters put into k-NN is captured in graphs of accuracy. Feature selection methods are compared under experimental conditions. Incremental learning on subset combinations is carried out in the gradual evolution of relative fault severities.

\item \textbf{knn-online.ipynb} - Simulate incremental learning process for the complete feature sets. The source domain for features is chosen in variable \emph{DOMAIN}. The progressive valuation of k-NN accuracy compares situations with varied sliding windows and gaps between annotated observations. The performance at the end of the training is written in tables.

\item \textbf{wavelets.ipynb} - Features computed from wavelet packet coefficients are chosen and sorted using feature selection scores. The effect of varying the depth of decomposition is viewed in stacked plots. The difference in scores between feature coefficients is plotted in bar charts.
\end{itemize}
